---
title: "Latihan_Porto_Netflix"
author: "Deswina"
date: '2022-07-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(readxl)
library(lubridate)
library(mice)
library(naniar)
library(tidyverse)
```
```{r}
netflix <- read_xlsx("Data/netflix_titles.xlsx")
  
```
```{r}
netflix
```
#Mengecek jumlah missing values
```{r}
sapply(netflix, function(x) sum(is.na(x)))

```
```{r}
netflix %>% 
  filter(is.na(duration) | is.na(rating) | is.na(date_added))
```

#Mengecek duplicates
```{r}
sum(duplicated(netflix))
```
```{r}
summary(netflix)
```
```{r}
miss_var_summary(netflix)
```
```{r}
miss_case_summary(netflix)
```
```{r}
df_netflix <- netflix %>% 
  select(-director) %>% 
  filter(!is.na(cast)) %>% 
  filter(!is.na(date_added)) %>% 
  filter(!is.na(country))
```
```{r}
miss_var_summary(df_netflix)
```
```{r}
df_netflix %>% 
  filter(is.na(duration))
```

```{r}
df_netflix <- df_netflix %>% 
  mutate(duration = case_when(show_id =="s5542" ~ "74 min",
                              show_id =="s5795" ~ "84 min",
                              show_id =="s5814" ~ "66 min",
                              TRUE ~ duration)) %>% 
  mutate(rating = case_when(show_id =="s5542" ~ "",
                              show_id =="s5795" ~ "",
                              show_id =="s5814" ~ "",
                              TRUE ~ rating)) 
 
df_netflix %>% 
 filter(show_id =="s5542" | show_id =="s5795" | show_id =="s5814")
```
```{r}
calc_mode <- function(x){
  
  # List the distinct / unique values
  distinct_values <- unique(x)
  
  # Count the occurrence of each distinct value
  distinct_tabulate <- tabulate(match(x, distinct_values))
  
  # Return the value with the highest occurrence
  distinct_values[which.max(distinct_tabulate)]
}
```
```{r}
  calc_mode(df_netflix$rating)
```
```{r}
df_netflix <- df_netflix %>% 
  mutate(rating = ifelse(is.na(rating), "TV-MA", rating)) %>% 
  mutate(rating = ifelse(rating == "", "TV-MA", rating))
    
```

```{r}
miss_var_summary(df_netflix)
```
```{r}
#df_netflix %>% 
 # separate(country, into = c('a','b','c','d','e','f','g','h','i','j','k','l')
  #       ,", ", convert = TRUE)
```
```{r}
remove(df_country)
```

#This is how you split the column of countries at the comma and then unest it into multiple rows
```{r}
 df_country <- df_netflix %>% 
    mutate(country = strsplit(as.character(country), ",")) %>% 
    unnest(country) %>%
      mutate(country = trimws(country, which = c("left"))) %>% #eliminate space on the left side
    filter(!is.na(country))
```
1. Where do the majority of movies available on Netflix come from?
```{r}
df_country %>% 
  group_by(country) %>% 
  filter(type == "Movie") %>% 
  summarise(total=n()) %>% 
  arrange(desc(total))
```

```{r}
df_country %>% 
  group_by(country) %>% 
  filter(type == "TV Show") %>% 
  summarise(total=n()) %>% 
  arrange(desc(total))
```
#This is how you split the column of cast at the comma and then unest it into multiple rows
```{r}
df_cast <- df_netflix %>% 
  select(c('show_id','type','title','cast','date_added','country','release_year','listed_in','duration')) %>% 
        gather(key = 'role', value = 'person', cast) %>% 
             filter(person != "") %>% separate_rows(person, sep = ',')
```
2. Who are the actors that appear in the most movies/shows?
```{r}
df_cast %>% 
  group_by(person) %>% 
  filter(type == "Movie") %>% 
  summarise(total = n()) %>% 
  arrange(desc(total))
```
```{r}
df_cast %>% 
  group_by(person) %>% 
  filter(type == "TV Show") %>% 
  summarise(total = n()) %>% 
  arrange(desc(total))
```
3. Which ones are the most abundant genres?
```{r}
 df_genre <-df_netflix %>% 
  select(c('show_id','type','title','cast','date_added','country','release_year','listed_in','duration')) %>% 
        gather(key = 'role', value = 'genre', listed_in) %>% 
             filter(genre != "") %>% 
              separate_rows(genre, sep = ',')
```

```{r}
df_genre %>% 
  group_by(genre) %>% 
  filter(type == "TV Show") %>% 
  summarise(total = n()) %>% 
  unique() %>% 
  arrange(desc(total))
```
```{r}
df_genre %>% 
  group_by(genre) %>% 
  filter(type == "Movie") %>% 
  summarise(total = n()) %>% 
  arrange(desc(total))
```
```



```{r}
#any(is.na(netflix))

#md.pattern(netflix)
```





























